Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-09 paper/paper.tex
typoe fixed

To justify the claim that Anglican is an \textit{efficient}
implementation, performance of Anglican programs must evaluated
both against Clojure programs and against inference tasks in
other probabilistic programming languages and environments.
Anglican passes two additional parameters to every function, adds
extra code to variable bindings, and passes every function
call through the trampoline. Hence difference in performance
between Anglican and Clojure should be most noticeable on
programs which involve many function calls. One such example is
the famous \textit{Towers of Hanoi}:

>>>>

To justify the claim that Anglican is an \textit{efficient}
implementation, performance of Anglican programs must be evaluated
both against Clojure programs and against inference tasks in
other probabilistic programming languages and environments.
Anglican passes two additional parameters to every function, adds
extra code to variable bindings, and passes every function
call through the trampoline. Hence difference in performance
between Anglican and Clojure should be most noticeable on
programs which involve many function calls. One such example is
the famous \textit{Towers of Hanoi}:
